---
title: "HW10"
author: "Angela Zhao"
output: pdf_document
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

```{r echo=FALSE,message=FALSE}
#load libraries
library(tidyverse)
library(mosaic)
library(moderndive)
library(effectsize)
#datasets
redline <- read_csv('redlining.csv')
grocery <- read_csv('groceries.csv')
```

az9934  
https://github.com/angela2zhao/HW10


# **Problem 1**
The question I am trying to answer is whether there is an association between the number of FAIR policies and the racial/ethnic composition of a ZIP code.  
The approach I took was fitting a linear model for the number of FAIR policies and using minority, fire, age, and income as variables. I looked at the confidence interval for the minority variable to check if the coefficient was statistically significant. I used the estimate to determine its relationship to the number of FAIR policies.
```{r echo = FALSE}
lm_red = lm(policies ~ minority + fire + age + income, data = redline)
get_regression_table(lm_red, conf.level = 0.95)
```
My conclusion is that there is an association between the number of FAIR policies and the racial/ethnic composition of a zip code. After adjusting for the fire, age, and income variables, I found that for every increase in 1% of residents that identified as a member of a racial/ethnic minority, there is an expected increase of 0.008 FAIR policies and renewals per 100 housing units in that ZIP code. The 95% confidence interval for this variable does not contain 0, so we can conclude that it is statistically significant. There is an increase in FAIR programs being used in areas with more racial/ethnic minorities, which implies less access to the private market in those areas.     

# **Problem 2**

# Part A
```{r echo = FALSE}
stores = grocery %>%
  group_by(Store) %>%
  summarize(avg_price = mean(Price))

ggplot(stores,aes(x=Store, y=avg_price)) + geom_col() + coord_flip() + labs(title="Price Differences Across Different Stores",y="Average Price of Products Sold at Store")
```
The graph above shows the average price of products for each store. 

# Part B
```{r echo = FALSE}
products = grocery %>%
  count(Product)

ggplot(products,aes(x=Product, y=n)) + geom_col() + coord_flip() + labs(title="Number of Stores Selling Each Product",y="Number of Stores Selling the Product")
```
The graph above shows the number of stores selling each product. 

# Part C
```{r echo = FALSE}
lm_type = lm(Price ~ Product + Type, data=grocery)
confint(lm_type)
```
Compared with ordinary grocery stores (like Albertsons, HEB, or Krogers), convenience stores charge somewhere between
\$0.41 and \$0.92 dollars more for the same product.

# Part D
```{r echo = FALSE}
lm_store = lm(Price ~ Product + Store, data=grocery)
coef(lm_store)
```
The two stores that seem to charge the lowest prices when comparing the same product are Walmart and Kroger Fresh Fare. The two stores that seem to charge the highest prices when comparing the same product are Whole Foods and Wheatsville Food Co-Op.

\newpage
# Part E
```{r echo = FALSE}
tail(get_regression_table(lm_store), 13)
```
Central Market charges a similar amount to HEB for the same product, with a coefficient of -0.573 for Central Market and -0.646 for HEB. There is a slight difference, but it is not that large compared to other coefficients, which go up to 0.3 or as low as -0.9. Their confidence intervals also overlap, which shows that their prices are similar.

# Part F
```{r echo = FALSE}
grocery = grocery %>%
  mutate(Income10k = Income%/%10000)
lm_income = lm(Price ~ Product + Income10k, data = grocery)
coef(lm_income)
standardize_parameters(lm_income)
```
The sign of the coefficient for Income10k is negative, which means that as income increases, the price of products decrease. This means that consumers in poorer zip codes seem to pay more for the same product.  
A one-standard deviation increase in the income of a ZIP code seems to be associated with a -0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.